### 2015-09-29 manuscript/content/conclusions.tex
Fixed typos.

We investigated the design of a general system that could be used for many applications, whether it be a BAC warning system, or a geographical mapping service that displays the smartwatch data of users on a chloropleth map. Part of this system was a general Android-based gateway that can be used to collect data from a variety of sensors connected to an Android smartphone.

>>>>

We investigated the design of a general system that could be used for many applications, whether it be a BAC warning system, or a geographical mapping service that displays the smartwatch data of users on a choropleth map. Part of this system was a general Android-based gateway that can be used to collect data from a variety of sensors connected to an Android smartphone.

### 2015-09-29 manuscript/content/system.tex
CV log. and SVM_1
Fixed typos.

Before we get into the specifics of looking into the data and the prediction of the intoxication level, let's take a quick look at the underlying infrastructure of our collection system. A huge end-goal of ours is to have a public system where participating users' phones transmit sensor information to a central database through a REST-based web service. The service stores this information in the database and another data processing system. Other users who are not contributing information can connect to our system to access other related services, like a chloropleth map of the sensor data; BAC prediction data in our case, but the system would not limited to it. The particular protocols and setup used should be designed to protect the privacy of the sensor data contributors.

>>>>

A huge end-goal of ours is to have a public system where participating users' phones transmit sensor information to a central database through a REST-based web service. The service stores this information in the database and another data processing system. Other users who are not contributing information can connect to our system to access other related services, like a choropleth map of the sensor data; BAC prediction data in our case, but the system would not be limited to it. The particular protocols and setup used should be designed to protect the privacy of the sensor data contributors.
